---
title: "misinformation analysis"
author: "Yimin"
date: "2025-03-06"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(readr)
library(ggplot2)
misinfo_d <- read_csv('../data/life-under-lockdown-wave2-extract (1).csv',
                     show_col_types = FALSE)

knowledge_levels <- c(
  'Nothing at all',
  'Not very much',
  'A great deal',
  'A fair amount'
)
misinfo_d <- misinfo_d %>%
  mutate(
    know_facebook = know_facebook %>%
      ordered(
        levels = knowledge_levels
      )
  )

```

# visualise
```{r visualise-age}
misinfo_d %>% 
  ggplot(
    aes(x = age)
  )+
  geom_histogram(binwidth = 5)

```


```{r visualise- gender}
misinfo_d %>%
  ggplot(
    aes(x = gender)
  )+
  geom_bar()
```


```{r visualise - know_facebook}
misinfo_d %>%
  ggplot(
    aes(x = know_facebook)
  )+
  geom_bar()
```

```{r visualise_beliefs}
misinfo_d %>%
  ggplot(
    aes(x = beliefs)
  )+
  geom_histogram(binwidth = 1)
```


# Analysis

H1 We expect a relationship between Gender and number of misinformation beliefs

```{r gender-beliefs-table}
misinfo_d %>%
  group_by(gender)%>%
  summarise(
    n = n(),
    M = mean(beliefs),
    Mdn = median(beliefs),
    SD = sd(beliefs)
  )
```

In the sample, men had more misinformation beliefs(M = .73, SD= 1.14)

```{r gender-beliefs-test}
misinfo_d %>%
  filter(gender != 'In another way')%>%
  t.test(
    beliefs ~ gender,
    data = .
  )
```


# Hypotheses
H1 We e

H2 We expect a relationship between age and number of misinformation beliefs

H3 We expect a relationship between relying on Facebook for knowledge 

# descriptive analysis
```{r age-beliefs analysis}
misinfo_d %>%
  ggplot(
  aes(x = age, y = beliefs)
)+
  geom_jitter()
  
```

```{r age-beliefs-correlation test}

misinfo_d %>%
  cor.test(
    ~age + beliefs,
    data = .,
    method = 'pearson'
  )
```
In the sample, there is a statistically significant moderate negative correlation between age and number of misinformation beliefs, r(498) = -.24, 95% CI [-.32,-.16] ,p < 0.001.


# Fingdings
```{r gender}
```
## number of misinformation beliefs reliance on Facebook for knowledge
```{r facebook-beliefs statiscs}
misinfo_d %>%
  ggplot(
    aes(x = know_facebook, y = beliefs)
  )+
  geom_boxplot()
```

```{r facebook-beliefs-correlation}
misinfo_d %>%
  mutate(
    know_facebook = as.numeric(know_facebook)
  ) %>%
  
  cor.test(
    ~know_facebook +beliefs,
    data = .,
    method = 'spearman',
    exact = FALSE
  )
```

In the sample ,there is a statistically significant moderate positive correlation between relying on Facebook for knowledge about coronavirus and number of misinformation beliefs, rs(498)=.23, p<0.01